%-----------------------------------------------------------------------------------------------------------------------------------------------%
%	The MIT License (MIT)
%
%	Copyright (c) 2021 Jitin Nair
%
%	Permission is hereby granted, free of charge, to any person obtaining a copy
%	of this software and associated documentation files (the "Software"), to deal
%	in the Software without restriction, including without limitation the rights
%	to use, copy, modify, merge, publish, distribute, sublicense, and/or sell
%	copies of the Software, and to permit persons to whom the Software is
%	furnished to do so, subject to the following conditions:
%	
%	THE SOFTWARE IS PROVIDED "AS IS", WITHOUT WARRANTY OF ANY KIND, EXPRESS OR
%	IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES OF MERCHANTABILITY,
%	FITNESS FOR A PARTICULAR PURPOSE AND NONINFRINGEMENT. IN NO EVENT SHALL THE
%	AUTHORS OR COPYRIGHT HOLDERS BE LIABLE FOR ANY CLAIM, DAMAGES OR OTHER
%	LIABILITY, WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE, ARISING FROM,
%	OUT OF OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR OTHER DEALINGS IN
%	THE SOFTWARE.
%	
%
%-----------------------------------------------------------------------------------------------------------------------------------------------%

%----------------------------------------------------------------------------------------
%	DOCUMENT DEFINITION
%----------------------------------------------------------------------------------------

% article class because we want to fully customize the page and not use a cv template
\documentclass[a4paper,12pt]{article}

%----------------------------------------------------------------------------------------
%	FONT
%----------------------------------------------------------------------------------------

% % fontspec allows you to use TTF/OTF fonts directly
% \usepackage{fontspec}
% \defaultfontfeatures{Ligatures=TeX}

% % modified for ShareLaTeX use
% \setmainfont[
% SmallCapsFont = Fontin-SmallCaps.otf,
% BoldFont = Fontin-Bold.otf,
% ItalicFont = Fontin-Italic.otf
% ]
% {Fontin.otf}

%----------------------------------------------------------------------------------------
%	PACKAGES
%----------------------------------------------------------------------------------------
\usepackage{url}
\usepackage{parskip} 	

%other packages for formatting
\RequirePackage{color}
\RequirePackage{graphicx}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage[scale=0.9]{geometry}

%tabularx environment
\usepackage{tabularx}

%for lists within experience section
\usepackage{enumitem}

% centered version of 'X' col. type
\newcolumntype{C}{>{\centering\arraybackslash}X} 

%to prevent spillover of tabular into next pages
\usepackage{supertabular}
\usepackage{tabularx}
\newlength{\fullcollw}
\setlength{\fullcollw}{0.47\textwidth}

%custom \section
\usepackage{titlesec}				
\usepackage{multicol}
\usepackage{multirow}

%CV Sections inspired by: 
%http://stefano.italians.nl/archives/26
\titleformat{\section}{\Large\scshape\raggedright}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{10pt}{10pt}

%for publications
\usepackage[style=authoryear,sorting=ynt, maxbibnames=2]{biblatex}

%Setup hyperref package, and colours for links
\usepackage[unicode, draft=false]{hyperref}
\definecolor{linkcolour}{rgb}{0,0.2,0.6}
\hypersetup{colorlinks,breaklinks,urlcolor=linkcolour,linkcolor=linkcolour}
\addbibresource{citations.bib}
\setlength\bibitemsep{1em}

%for social icons
\usepackage{fontawesome5}

%debug page outer frames
%\usepackage{showframe}


% job listing environments
\newenvironment{jobshort}[2]
    {
    \begin{tabularx}{\linewidth}{@{}l X r@{}}
    \textbf{#1} & \hfill &  #2 \\[3.75pt]
    \end{tabularx}
    }
    {
    }

\newenvironment{joblong}[2]
    {
    \begin{tabularx}{\linewidth}{@{}l X r@{}}
    \textbf{#1} & \hfill &  #2 \\[3.75pt]
    \end{tabularx}
    \begin{minipage}[t]{\linewidth}
    \begin{itemize}[nosep,after=\strut, leftmargin=1em, itemsep=3pt,label=--]
    }
    {
    \end{itemize}
    \end{minipage}    
    }

%----------------------------------------------------------------------------------------
%	BEGIN DOCUMENT
%----------------------------------------------------------------------------------------
\begin{document}

% non-numbered pages
\pagestyle{empty} 

%----------------------------------------------------------------------------------------
%	TITLE
%----------------------------------------------------------------------------------------

% \begin{tabularx}{\linewidth}{ @{}X X@{} }
% \huge{Your Name}\vspace{2pt} & \hfill \emoji{incoming-envelope} email@email.com \\
% \raisebox{-0.05\height}\faGithub\ username \ | \
% \raisebox{-0.00\height}\faLinkedin\ username \ | \ \raisebox{-0.05\height}\faGlobe \ mysite.com  & \hfill \emoji{calling} number
% \end{tabularx}

\begin{tabularx}{\linewidth}{@{} C @{}}
\Huge{Siddhartha Shakya} \\[7.5pt]
\href{https://github.com/SiddhuShkya}{\raisebox{-0.05\height}\faGithub\ GitHub} \ $|$ \ 
\href{https://www.linkedin.com/in/siddhartha-shakya-5665a0236/}{\raisebox{-0.05\height}\faLinkedin\ Linkedin} \ $|$ \ 
\href{mailto:siddhuushakyaa@gmail.com}{\raisebox{-0.05\height}\faEnvelope \ siddhuushakyaa@gmail.com} \ $|$ \ 
\href{tel:+977 9810367988}{\raisebox{-0.05\height}\faMobile \ +977 9810367988} \\
\end{tabularx}

%----------------------------------------------------------------------------------------
% EXPERIENCE SECTIONS
%----------------------------------------------------------------------------------------

%Interests/ Keywords/ Summary
\section{Summary}
AI \& Data Engineering graduate with hands-on experience in ML development, ETL pipeline orchestration, and MLOps. Demonstrated ability to build end-to-end solutions through an AI internship and independent projects spanning data engineering, NLP, and model deployment. Eager to contribute and grow in a junior Data Engineer or ML Engineer role.

%Experience
\section{Work Experience}
\begin{joblong}{AI Intern $|$ \normalfont\textit{Mach24 Orbitals}}{Oct 2025 - Feb 2026}
\item Built Streamlit dashboard for environmental monitoring using Landsat-8, performing time series analysis on vegetation indices, land surface temperature, and urbanization patterns.
\item Researched ML approaches for Above Ground Biomass estimation using Sentinel-2 imagery via Google Earth Engine API, evaluating regression models for biomass prediction from remote sensing data.
\end{joblong}

\begin{joblong}{Graduate Teaching Assistant $|$ \normalfont\textit{Herald College Kathmandu}}{Aug 2024 - Sep 2025}
\item Led workshop sessions on parallel computing and performance optimization, covering parallel programming paradigms and GPU computing. 
\item Conducted tutorials on Big Data technologies along with practical labs covering Hadoop ecosystem, MapReduce programming, distributed data processing frameworks, and real-time streaming. Guided students through implementation exercises involving large-scale data analysis and processing techniques.
\end{joblong}
%Projects
\vspace{-20pt}
\section{Projects}

\begin{tabularx}{\linewidth}{ @{}l r@{} }
\textbf{Weather ETL Pipeline} & \hfill \href{https://github.com/SiddhuShkya/Extract-Transform-Load}{Repo Link} \\[3.75pt]
\multicolumn{2}{@{}X@{}}{Developed a fully automated ETL pipeline to ingest weather data. Engineered a containerized infrastructure with Docker Compose to orchestrate nested data transformations and loading into PostgreSQL, implementing robust error-handling and deduplication logic for 100\% data reliability.

\textbf{Tech Stack:} Apache Airflow, Python, PostgreSQL, PgAdmin, Docker, Docker Compose, Astronomer, Git, OPEN METEO API. }  \\
\end{tabularx}

\begin{tabularx}{\linewidth}{ @{}l r@{} }
\textbf{Movie Recommendation System} & \hfill \href{https://github.com/SiddhuShkya/Movie-Recommendation-System}{Repo Link} \\[3.75pt]
\multicolumn{2}{@{}X@{}}{Built a semantic movie recommendation engine using Transformer embeddings across 13,000+ titles. Implemented unified logging system tracking data ingestion, cleaning, and model training. Optimized deployment with multi-stage Docker setup and automated CI/CD testing using GitHub Actions and Pytest.

\textbf{Tech Stack:}  Python, HuggingFace, Scikit-learn, NLTK, FastAPI, Jinja2, Docker, Docker Compose, GitHub Actions (CI), Pytest, logging.}  \\
\end{tabularx}

\begin{tabularx}{\linewidth}{ @{}l r@{} }
\textbf{Text Summarization MLOps Pipeline} & \hfill \href{https://github.com/SiddhuShkya/Text-Summarizer-With-HF}{Repo Link} \\[3.75pt]
\multicolumn{2}{@{}X@{}}{Built an automated text summarization pipeline using NLP models to convert long-form text and dialogues into concise summaries through a multi-stage MLOps workflow.

\textbf{Tech Stack:}  Python, FastAPI, PyTorch, HuggingFace, NLTK, ROUGE, Docker, Docker Compose, Git, GitHub Actions (CI/CD), Pandas, PyYAML.}  \\
\end{tabularx}

%----------------------------------------------------------------------------------------
%	EDUCATION
%----------------------------------------------------------------------------------------
\section{Education}
\begin{tabularx}{\linewidth}{@{}l X@{}}
2026 - present & PG Diploma in Data Science at \textbf{Manipal University} \\

2022 - 2024 & BSc (Hons) in Computer Science at \textbf{Herald College} \hfill (Awards: First Class Honors) \\ 
\end{tabularx}

%----------------------------------------------------------------------------------------
%	CERTIFICATIONS
%----------------------------------------------------------------------------------------
\section{Certifications}
\begin{tabularx}{\linewidth}{@{}l X r@{}}
\textbf{The Complete SQL Bootcamp: Zero to Hero} & \normalsize{Udemy} & \hfill 2026 \\
\textbf{Complete MLOps Bootcamp} & \normalsize{Udemy} & \hfill 2026 \\
\end{tabularx}

%----------------------------------------------------------------------------------------
%	SKILLS
%----------------------------------------------------------------------------------------
\section{Skills}
\begin{tabularx}{\linewidth}{@{}l X@{}}
\textbf{Programming Languages} &  \normalsize{Python, SQL, Java, C/C++, Bash/Shell}\\
\textbf{Databases} &  \normalsize{PostgreSQL, MongoDB, MySQL, Redis}\\ 
\textbf{Cloud Platforms} &  \normalsize{AWS, Google Cloud Platform (GCP)}\\
\textbf{AI \& ML Frameworks} &  \normalsize{PyTorch, HuggingFace Transformers, Keras, Scikit-learn}\\
\textbf{Data Visualization \& BI} &  \normalsize{Matplotlib, Seaborn, Plotly, Excel}\\
\textbf{Data Engineering} &  \normalsize{Apache Airflow, Apache Spark, Hadoop, ETL Pipelines, Pandas}\\
\textbf{DevOps \& MLOps} &  \normalsize{Docker, Docker Compose, Git, GitHub Actions (CI/CD), MLflow, DVC, YAML}\\
\end{tabularx}

\vfill
\begin{center}
\footnotesize Last updated: \today
\end{center}

\end{document}
