%-----------------------------------------------------------------------------------------------------------------------------------------------%
%	The MIT License (MIT)
%
%	Copyright (c) 2021 Jitin Nair
%
%	Permission is hereby granted, free of charge, to any person obtaining a copy
%	of this software and associated documentation files (the "Software"), to deal
%	in the Software without restriction, including without limitation the rights
%	to use, copy, modify, merge, publish, distribute, sublicense, and/or sell
%	copies of the Software, and to permit persons to whom the Software is
%	furnished to do so, subject to the following conditions:
%	
%	THE SOFTWARE IS PROVIDED "AS IS", WITHOUT WARRANTY OF ANY KIND, EXPRESS OR
%	IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES OF MERCHANTABILITY,
%	FITNESS FOR A PARTICULAR PURPOSE AND NONINFRINGEMENT. IN NO EVENT SHALL THE
%	AUTHORS OR COPYRIGHT HOLDERS BE LIABLE FOR ANY CLAIM, DAMAGES OR OTHER
%	LIABILITY, WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE, ARISING FROM,
%	OUT OF OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR OTHER DEALINGS IN
%	THE SOFTWARE.
%	
%
%-----------------------------------------------------------------------------------------------------------------------------------------------%

%----------------------------------------------------------------------------------------
%	DOCUMENT DEFINITION
%----------------------------------------------------------------------------------------

% article class because we want to fully customize the page and not use a cv template
\documentclass[a4paper,12pt]{article}

%----------------------------------------------------------------------------------------
%	FONT
%----------------------------------------------------------------------------------------

% % fontspec allows you to use TTF/OTF fonts directly
% \usepackage{fontspec}
% \defaultfontfeatures{Ligatures=TeX}

% % modified for ShareLaTeX use
% \setmainfont[
% SmallCapsFont = Fontin-SmallCaps.otf,
% BoldFont = Fontin-Bold.otf,
% ItalicFont = Fontin-Italic.otf
% ]
% {Fontin.otf}

%----------------------------------------------------------------------------------------
%	PACKAGES
%----------------------------------------------------------------------------------------
\usepackage{url}
\usepackage{parskip} 	

%other packages for formatting
\RequirePackage{color}
\RequirePackage{graphicx}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage[scale=0.9]{geometry}

%tabularx environment
\usepackage{tabularx}

%for lists within experience section
\usepackage{enumitem}

% centered version of 'X' col. type
\newcolumntype{C}{>{\centering\arraybackslash}X} 

%to prevent spillover of tabular into next pages
\usepackage{supertabular}
\usepackage{tabularx}
\newlength{\fullcollw}
\setlength{\fullcollw}{0.47\textwidth}

%custom \section
\usepackage{titlesec}				
\usepackage{multicol}
\usepackage{multirow}

%CV Sections inspired by: 
%http://stefano.italians.nl/archives/26
\titleformat{\section}{\Large\scshape\raggedright}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{10pt}{10pt}

%for publications
\usepackage[style=authoryear,sorting=ynt, maxbibnames=2]{biblatex}

%Setup hyperref package, and colours for links
\usepackage[unicode, draft=false]{hyperref}
\definecolor{linkcolour}{rgb}{0,0.2,0.6}
\hypersetup{colorlinks,breaklinks,urlcolor=linkcolour,linkcolor=linkcolour}
\addbibresource{citations.bib}
\setlength\bibitemsep{1em}

%for social icons
\usepackage{fontawesome5}

%debug page outer frames
%\usepackage{showframe}


% job listing environments
\newenvironment{jobshort}[2]
    {
    \begin{tabularx}{\linewidth}{@{}l X r@{}}
    \textbf{#1} & \hfill &  #2 \\[3.75pt]
    \end{tabularx}
    }
    {
    }

\newenvironment{joblong}[2]
    {
    \begin{tabularx}{\linewidth}{@{}l X r@{}}
    \textbf{#1} & \hfill &  #2 \\[3.75pt]
    \end{tabularx}
    \begin{minipage}[t]{\linewidth}
    \begin{itemize}[nosep,after=\strut, leftmargin=1em, itemsep=3pt,label=--]
    }
    {
    \end{itemize}
    \end{minipage}    
    }

%----------------------------------------------------------------------------------------
%	BEGIN DOCUMENT
%----------------------------------------------------------------------------------------
\begin{document}

% non-numbered pages
\pagestyle{empty} 

%----------------------------------------------------------------------------------------
%	TITLE
%----------------------------------------------------------------------------------------

% \begin{tabularx}{\linewidth}{ @{}X X@{} }
% \huge{Your Name}\vspace{2pt} & \hfill \emoji{incoming-envelope} email@email.com \\
% \raisebox{-0.05\height}\faGithub\ username \ | \
% \raisebox{-0.00\height}\faLinkedin\ username \ | \ \raisebox{-0.05\height}\faGlobe \ mysite.com  & \hfill \emoji{calling} number
% \end{tabularx}

\begin{tabularx}{\linewidth}{@{} C @{}}
\Huge{Siddhartha Shakya} \\[7.5pt]
\href{https://github.com/SiddhuShkya}{GitHub} $|$ \ 
\href{https://www.linkedin.com/in/sidShkya/}{LinkedIn} $|$ \
\href{mailto:siddhuushakyaa@gmail.com}{siddhuushakyaa@gmail.com} \ $|$ \ 
\href{tel:+971548889367}{+971 54 888 9367} \ $|$ \ 
\href{https://maps.google.com/?q=International+City,+Dubai}{Dubai, UAE} \\
\end{tabularx}

%----------------------------------------------------------------------------------------
% EXPERIENCE SECTIONS
%----------------------------------------------------------------------------------------

%Interests/ Keywords/ Summary
\section{Summary}
Data engineer building end-to-end pipelines from raw data through production dashboards, with hands-on ML deployment experience. Proven ability to architect scalable ETL systems, evaluate ML models in production, and deliver solutions that enable real-time insights at scale. Seeking entry-level Data or AI engineering role in Dubai.

%Experience
\section{Work Experience}
\begin{joblong}{AI Intern $|$ \normalfont\textit{Mach24 Orbitals}}{Oct 2025 - Feb 2026}
\item Built and deployed a Streamlit dashboard on GCP processing Landsat-8 satellite imagery across 5+ years of time series data; enabled real-time visualization of vegetation indices, land surface temperature, and urbanization patterns for environmental monitoring. Dashboard processes 1,000+ imagery tiles monthly with 200ms average load time.
\item Evaluated 3+ regression models (Random Forest, XGBoost, SVM) for Above Ground Biomass (AGB) estimation using Sentinel-2 imagery via Google Earth Engine API across 450+ test plots. XGBoost achieved 23\% lower RMSE than Random Forest baseline (RMSE: 14.2 vs. 18.5 Mg/ha), identified as production candidate for scaled deployment.    
\end{joblong}

\begin{joblong}{Graduate Teaching Assistant $|$ \normalfont\textit{Herald College Kathmandu}}{Aug 2024 - Sep 2025}
\item Led 8+ workshop sessions on parallel computing and performance optimization, instructing 50+ students across programming paradigms and GPU computing fundamentals; direct feedback integration improved student assessment scores by 15\%. 
\item Conducted hands-on labs and tutorials on Big Data technologies covering Hadoop ecosystem (HDFS, MapReduce), distributed processing frameworks (Spark), and real-time streaming pipelines; designed and graded practical assignments for 3+ cohorts (~120 students total).
\end{joblong}
%Projects
\section{Projects}

\begin{tabularx}{\linewidth}{ @{}l r@{} }
\textbf{Weather ETL Pipeline} & \hfill \href{https://github.com/SiddhuShkya/Extract-Transform-Load}{Repo Link} \\[3.75pt]
\multicolumn{2}{@{}X@{}}{Built production ETL pipeline ingesting 50,000+ weather records daily from Open-Meteo API into PostgreSQL via Apache Airflow (99.2\% uptime). Implements deduplication, error handling, and retry logic; deployed on GCP Compute Engine with Docker Compose, automated health checks, and logging. Enables real-time analytics for downstream ML models.

\textbf{Tech Stack:} Apache Airflow, Python, PostgreSQL, PgAdmin, Docker, Docker Compose, Astronomer, Git, OPEN METEO API. }  \\
\end{tabularx}

\begin{tabularx}{\linewidth}{ @{}l r@{} }
\textbf{Movie Recommendation System} & \hfill \href{https://github.com/SiddhuShkya/Movie-Recommendation-System}{Repo Link} \\[3.75pt]
\multicolumn{2}{@{}X@{}}{Built a semantic movie recommendation engine using Transformer embeddings across 13,000+ titles. Implemented unified logging system tracking data ingestion, cleaning, and model training. Optimized deployment with multi-stage Docker setup and automated CI/CD testing using GitHub Actions and Pytest.

\textbf{Tech Stack:}  Python, HuggingFace, Scikit-learn, NLTK, FastAPI, Jinja2, Docker, Docker Compose, GitHub Actions (CI), Pytest, logging.}  \\
\end{tabularx}

\begin{tabularx}{\linewidth}{ @{}l r@{} }
\textbf{Text Summarization MLOps Pipeline} & \hfill \href{https://github.com/SiddhuShkya/Text-Summarizer-With-HF}{Repo Link} \\[3.75pt]
\multicolumn{2}{@{}X@{}}{Built an automated text summarization pipeline using NLP models to convert long-form text and dialogues into concise summaries through a multi-stage MLOps workflow.

\textbf{Tech Stack:}  Python, FastAPI, PyTorch, HuggingFace, NLTK, ROUGE, Docker, Docker Compose, Git, GitHub Actions (CI/CD), Pandas, PyYAML.}  \\
\end{tabularx}

%----------------------------------------------------------------------------------------
%	EDUCATION
%----------------------------------------------------------------------------------------
\section{Education}
\begin{tabularx}{\linewidth}{@{}l X@{}}
2026 - present & PG Diploma in Data Science at \textbf{Manipal University} \\

2022 - 2024 & BSc (Hons) in Computer Science at \textbf{Herald College} \hfill (Awards: First Class Honors) \\ 
\end{tabularx}

%----------------------------------------------------------------------------------------
%	CERTIFICATIONS
%----------------------------------------------------------------------------------------
\section{Certifications}
\begin{tabularx}{\linewidth}{@{}l X r@{}}
\textbf{The Complete SQL Bootcamp: Zero to Hero} & \normalsize{Udemy} & \hfill 2026 \\
\textbf{Complete MLOps Bootcamp} & \normalsize{Udemy} & \hfill 2025 \\
\end{tabularx}

%----------------------------------------------------------------------------------------
%	SKILLS
%----------------------------------------------------------------------------------------
\section{Skills}
\begin{tabularx}{\linewidth}{@{}l X@{}}
\textbf{Programming} &  \normalsize{Python, SQL, C/C++, Bash/Shell}\\
\textbf{Databases} &  \normalsize{PostgreSQL, MongoDB, MySQL}\\ 
\textbf{Cloud Platforms} &  \normalsize{AWS, Google Cloud Platform (GCP)}\\
\textbf{DevOps \& MLOps} &  \normalsize{Docker, Git \& GitHub Actions (CI/CD), MLflow, DVC}\\
\textbf{AI \& ML} &  \normalsize{PyTorch, HuggingFace Transformers, Scikit-learn}\\
\textbf{Data Engineering} &  \normalsize{Apache Airflow, Apache Spark, Hadoop, Pandas, NumPy}\\
\textbf{Data Visualization} & \normalsize{Matplotlib, Seaborn, Excel, Plotly, Power BI, Tableau}\\
\end{tabularx}

\vfill
\begin{center}
\footnotesize Last updated: \today
\end{center}

\end{document}
