%-----------------------------------------------------------------------------------------------------------------------------------------------%
%	The MIT License (MIT)
%
%	Copyright (c) 2021 Jitin Nair
%
%	Permission is hereby granted, free of charge, to any person obtaining a copy
%	of this software and associated documentation files (the "Software"), to deal
%	in the Software without restriction, including without limitation the rights
%	to use, copy, modify, merge, publish, distribute, sublicense, and/or sell
%	copies of the Software, and to permit persons to whom the Software is
%	furnished to do so, subject to the following conditions:
%	
%	THE SOFTWARE IS PROVIDED "AS IS", WITHOUT WARRANTY OF ANY KIND, EXPRESS OR
%	IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES OF MERCHANTABILITY,
%	FITNESS FOR A PARTICULAR PURPOSE AND NONINFRINGEMENT. IN NO EVENT SHALL THE
%	AUTHORS OR COPYRIGHT HOLDERS BE LIABLE FOR ANY CLAIM, DAMAGES OR OTHER
%	LIABILITY, WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE, ARISING FROM,
%	OUT OF OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR OTHER DEALINGS IN
%	THE SOFTWARE.
%	
%
%-----------------------------------------------------------------------------------------------------------------------------------------------%

%----------------------------------------------------------------------------------------
%	DOCUMENT DEFINITION
%----------------------------------------------------------------------------------------

% article class because we want to fully customize the page and not use a cv template
\documentclass[a4paper,11pt]{article}

%----------------------------------------------------------------------------------------
%	FONT
%----------------------------------------------------------------------------------------

% % fontspec allows you to use TTF/OTF fonts directly
% \usepackage{fontspec}
% \defaultfontfeatures{Ligatures=TeX}

% % modified for ShareLaTeX use
% \setmainfont[
% SmallCapsFont = Fontin-SmallCaps.otf,
% BoldFont = Fontin-Bold.otf,
% ItalicFont = Fontin-Italic.otf
% ]
% {Fontin.otf}

%----------------------------------------------------------------------------------------
%	PACKAGES
%----------------------------------------------------------------------------------------
\usepackage{url}
\usepackage{parskip} 	

%other packages for formatting
\RequirePackage{color}
\RequirePackage{graphicx}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage[scale=0.91]{geometry}

%tabularx environment
\usepackage{tabularx}

%for lists within experience section
\usepackage{enumitem}

% centered version of 'X' col. type
\newcolumntype{C}{>{\centering\arraybackslash}X} 

%to prevent spillover of tabular into next pages
\usepackage{supertabular}
\usepackage{tabularx}
\newlength{\fullcollw}
\setlength{\fullcollw}{0.47\textwidth}

%custom \section
\usepackage{titlesec}				
\usepackage{multicol}
\usepackage{multirow}

%CV Sections inspired by: 
%http://stefano.italians.nl/archives/26
\titleformat{\section}{\Large\scshape\raggedright}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{10pt}{10pt}

%for publications
\usepackage[style=authoryear,sorting=ynt, maxbibnames=2]{biblatex}

%Setup hyperref package, and colours for links
\usepackage[unicode, draft=false]{hyperref}
\definecolor{linkcolour}{rgb}{0,0.2,0.6}
\hypersetup{colorlinks,breaklinks,urlcolor=linkcolour,linkcolor=linkcolour}
\addbibresource{citations.bib}
\setlength\bibitemsep{1em}

%for social icons
\usepackage{fontawesome5}

%debug page outer frames
%\usepackage{showframe}


% job listing environments
\newenvironment{jobshort}[2]
    {
    \begin{tabularx}{\linewidth}{@{}l X r@{}}
    \textbf{#1} & \hfill &  #2 \\[3.75pt]
    \end{tabularx}
    }
    {
    }

\newenvironment{joblong}[2]
    {
    \begin{tabularx}{\linewidth}{@{}l X r@{}}
    \textbf{#1} & \hfill &  #2 \\[3.75pt]
    \end{tabularx}
    \begin{minipage}[t]{\linewidth}
    \begin{itemize}[nosep,after=\strut, leftmargin=1em, itemsep=3pt,label=--]
    }
    {
    \end{itemize}
    \end{minipage}    
    }

%----------------------------------------------------------------------------------------
%	BEGIN DOCUMENT
%----------------------------------------------------------------------------------------
\begin{document}

% non-numbered pages
\pagestyle{empty} 

%----------------------------------------------------------------------------------------
%	TITLE
%----------------------------------------------------------------------------------------

% \begin{tabularx}{\linewidth}{ @{}X X@{} }
% \huge{Your Name}\vspace{2pt} & \hfill \emoji{incoming-envelope} email@email.com \\
% \raisebox{-0.05\height}\faGithub\ username \ | \
% \raisebox{-0.00\height}\faLinkedin\ username \ | \ \raisebox{-0.05\height}\faGlobe \ mysite.com  & \hfill \emoji{calling} number
% \end{tabularx}

\begin{tabularx}{\linewidth}{@{} C @{}} \Huge{Siddhartha Shakya} \\[7.5pt] 
\href{https://github.com/SiddhuShkya}{\raisebox{-0.05\height}\faGithub\ GitHub} \ $|$ \ 
\href{https://www.linkedin.com/in/siddhartha-shakya-5665a0236/}{\raisebox{-0.05\height}\faLinkedin\ Linkedin} \ $|$ \ 
\href{mailto:siddhuushakyaa@gmail.com}{\raisebox{-0.05\height}\faEnvelope \ siddhuushakyaa@gmail.com} \ $|$ \ 
\href{tel:+971548889367}{\raisebox{-0.05\height}\faMobile \ +971 548889367} \ $|$ \ 
\href{https://maps.google.com/?q=International+City,+Dubai}{\raisebox{-0.05\height}\faMapMarker \ Dubai, International City}
\end{tabularx}

%----------------------------------------------------------------------------------------
% EXPERIENCE SECTIONS
%----------------------------------------------------------------------------------------

%Interests/ Keywords/ Summary
\section{Summary}
Computer Science graduate with practical experience across the full data lifecycle, from building automated ETL pipelines to deploying NLP models in production. Gained real-world exposure through an
AI internship and teaching assistantship, with a strong foundation in both data engineering and machine
learning. Looking to bring these skills to an entry-level Data or AI engineering role.

%----------------------------------------------------------------------------------------
%	SKILLS
%----------------------------------------------------------------------------------------
\section{Skills}
\begin{tabularx}{\linewidth}{@{}l X@{}}
\textbf{Programming} &  \normalsize{Python, SQL, C/C++, Bash/Shell}\\
\textbf{Databases} &  \normalsize{PostgreSQL, MongoDB, MySQL}\\ 
\textbf{Cloud Platforms} &  \normalsize{AWS, Google Cloud Platform (GCP)}\\
\textbf{Data Engineering} &  \normalsize{Apache Airflow, Apache Spark, Hadoop, Pandas, NumPy}\\
\textbf{DevOps \& MLOps} &  \normalsize{Docker, Docker Compose, Git, GitHub Actions (CI/CD), MLflow, DVC}\\
\textbf{AI \& ML} &  \normalsize{PyTorch, HuggingFace Transformers, Scikit-learn}\\


\end{tabularx}

%----------------------------------------------------------------------------------------
% EXPERIENCE SECTIONS
%----------------------------------------------------------------------------------------

%Experience
\section{Work Experience}

\begin{joblong}{AI Intern $|$ \normalfont\textit{Mach24 Orbitals}}{Oct 2025 -- Feb 2026}
\item Built a Streamlit dashboard processing Landsat-8 satellite imagery across 5+ years of time series data, enabling real-time visualization of vegetation indices, land surface temperature, and urbanization patterns for environmental monitoring.
\item Evaluated 3+ regression models (Random Forest, XGBoost, SVM) for Above Ground Biomass estimation using Sentinel-2 imagery via Google Earth Engine API, identifying XGBoost as the top performer with the lowest RMSE across test plots.
\end{joblong}

\begin{joblong}{Graduate Assistant $|$ \normalfont\textit{Herald College Kathmandu}}{Aug 2024 -- Sep 2025}
\item Led workshop sessions on parallel computing and performance optimization, covering parallel programming paradigms and GPU computing. 
\item Conducted tutorials on Big Data technologies along with practical labs covering Hadoop ecosystem, MapReduce programming, distributed data processing frameworks, and real-time streaming.
\end{joblong}
%Projects
\vspace{-15pt}
\section{Projects}

\begin{tabularx}{\linewidth}{ @{}l r@{} }
\textbf{Weather ETL Pipeline} & \hfill \href{https://github.com/SiddhuShkya/Extract-Transform-Load}{Repo Link} \\[2pt]
\multicolumn{2}{@{}X@{}}{Automated end-to-end ETL pipeline ingesting live weather data from the Open-Meteo API, processing and loading into PostgreSQL with deduplication logic, error handling, and retry mechanisms. Containerized with Docker Compose and orchestrated via Apache Airflow with daily DAG scheduling.

\textbf{Tech Stack:} Apache Airflow, Python, PostgreSQL, PgAdmin, Docker, Docker Compose, Astronomer,
Git, OPEN METEO API.}  \\
\end{tabularx}

\begin{tabularx}{\linewidth}{ @{}l r@{} }
\textbf{Movie Recommendation System} & \hfill \href{https://github.com/SiddhuShkya/Movie-Recommendation-System}{Repo Link} \\[2pt]
\multicolumn{2}{@{}X@{}}{ontent-based recommendation engine across 13,000+ movie titles using HuggingFace Transformer embeddings for semantic similarity, served via a FastAPI backend. Deployed with multi-stage Docker builds, achieving sub-200ms response times, with automated CI/CD testing via GitHub Actions and Pytest.

\textbf{Tech Stack:} Python, HuggingFace, Scikit-learn, NLTK, FastAPI, Jinja2, Docker, Docker Compose,
GitHub Actions (CI), Pytest, logging.}  \\
\end{tabularx}

%----------------------------------------------------------------------------------------
%	EDUCATION
%----------------------------------------------------------------------------------------
\section{Education}
\begin{tabularx}{\linewidth}{@{}l X@{}}
2026 - pres. & PG Diploma in Data Science, \textbf{Manipal University} \\
2022 - 2024 & BSc (Hons) Computer Science, \textbf{Herald College} \hfill (First Class Honors) \\ 
\end{tabularx}
\begin{center}
\footnotesize Last updated: \today
\end{center}
\end{document}
