\documentclass[11pt,a4paper]{article}
% -------------------------------------------------
% Packages
% -------------------------------------------------
\usepackage[top=12mm,bottom=12mm,left=15mm,right=15mm]{geometry} 
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[UKenglish]{babel}
\usepackage{ragged2e}
\usepackage[stretch=25,shrink=25]{microtype}
\usepackage{xcolor}
\usepackage{graphicx}
\usepackage{fontawesome}
\usepackage{hyperref}

% -------------------------------------------------
% Colors and Setup
% -------------------------------------------------
\definecolor{cvteal}{HTML}{008080}
\definecolor{cvblue}{HTML}{304263}
\hypersetup{
    colorlinks=true,
    urlcolor=black,
    linkcolor=black
}
\setlength{\parindent}{0pt}         
\setlength{\parskip}{0.5em}         

% -------------------------------------------------
% !! EDIT THIS to change the role on the cover letter
% -------------------------------------------------
\newcommand{\jobrole}{Data Analyst}

% -------------------------------------------------
\begin{document}
\pagestyle{empty}

%==================================================
% Header
%==================================================
\begin{minipage}[b]{0.52\textwidth}
{\Huge\scshape\color{cvblue} Siddhartha Shakya}\\ [1.5mm]
{\Large\color{gray} \faGraduationCap\  BSc (Hons) Computer Science}
\end{minipage}
\hfill
\begin{minipage}[b]{0.43\textwidth}
\RaggedLeft\small
\setlength{\baselineskip}{14pt}
\mbox{\faMobile\ +971 55 183 0660}\\
\mbox{\faHome\ Dubai, UAE}\\
\mbox{\faEnvelope\ \href{mailto:siddhuushakyaa@gmail.com}{siddhuushakyaa@gmail.com}}\\
\mbox{\faLinkedinSquare\ \href{https://linkedin.com/in/sidShkya}{linkedin.com/in/sidShkya}}\\
\mbox{\faGithub\ \href{https://github.com/SiddhuShkya}{github.com/SiddhuShkya}}
\end{minipage}

\vspace{1mm}
{\color{cvteal}\rule{\linewidth}{1mm}} 
\vspace{2mm}

%==================================================
% Recipient & Date
%==================================================
\begin{flushleft}
    \textbf{Hiring Manager} \\
    The Company \\
    Dubai, UAE \\
    \vspace{1mm}
    14 July 2026
\end{flushleft}

\vspace{1mm}

%==================================================
% Letter Body
%==================================================
Dear Hiring Manager,\\

\begin{center}{\textbf{Position:} \underline{\jobrole}}\end{center}

\justifying

I am writing to express my strong interest in the \jobrole{} role at your company. As a First-Class Honours Computer Science graduate currently pursuing a PG Diploma in Data Science, I bring a proven ability to engineer production-grade data pipelines, apply machine learning at scale, and translate analytical findings into clear, actionable business insight. I am confident my hands-on background makes me a strong fit for a results-driven data science team.

My core technical strengths lie in Python and SQL, which I apply across the full data lifecycle --- from ingestion and cleaning through to modelling and visualisation. During my AI internship at Mach24 Orbitals, I built an automated end-to-end geospatial data pipeline using the Google Earth Engine API, eliminating manual processing and significantly reducing time-to-insight for satellite imagery analysis. Complementing this, my EduFin Investigation project demonstrates my analytical depth: I engineered PySpark and SQL pipelines in Databricks to analyse a 15,000+ student loan portfolio and surfaced a Rs.\ 12 Crore financial discrepancy through rigorous segmentation analysis --- a direct example of data science creating tangible commercial impact.

Beyond individual analysis, I have strong data engineering foundations that allow me to deliver reliable, scalable solutions. I architected a production-ready Medallion Architecture (Bronze/Silver/Gold) ELT pipeline for NYC parking violation data using dbt Core and DuckDB, with automated CI/CD deployments via GitHub Actions. My experience with Docker, MLflow, Airflow, and Snowflake further ensures I can operate effectively across modern cloud and MLOps stacks. I believe clean, well-tested data infrastructure is the foundation of any trustworthy data science function, and I take pride in building it right.

I am equally committed to communicating data clearly. As a Graduate Teaching Assistant, I designed and delivered Big Data and HPC curriculum to over 120 students, consistently translating complex technical concepts into accessible, practical learning. I am excited to bring the same clarity to cross-functional stakeholders at your company --- bridging the gap between data science outputs and business decisions. I would welcome the chance to discuss how my skills can contribute to your team's goals, and I look forward to the opportunity for an interview.

\vspace{3mm}

Best regards, \\
\textbf{Siddhartha Shakya}

%==================================================
% Footer
%==================================================
\vfill
{\color{cvteal}\rule{\linewidth}{1mm}}

\end{document}