%-----------------------------------------------------------------------------------------------------------------------------------------------%
%	The MIT License (MIT)
%
%	Copyright (c) 2021 Jitin Nair
%
%	Permission is hereby granted, free of charge, to any person obtaining a copy
%	of this software and associated documentation files (the "Software"), to deal
%	in the Software without restriction, including without limitation the rights
%	to use, copy, modify, merge, publish, distribute, sublicense, and/or sell
%	copies of the Software, and to permit persons to whom the Software is
%	furnished to do so, subject to the following conditions:
%	
%	THE SOFTWARE IS PROVIDED "AS IS", WITHOUT WARRANTY OF ANY KIND, EXPRESS OR
%	IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES OF MERCHANTABILITY,
%	FITNESS FOR A PARTICULAR PURPOSE AND NONINFRINGEMENT. IN NO EVENT SHALL THE
%	AUTHORS OR COPYRIGHT HOLDERS BE LIABLE FOR ANY CLAIM, DAMAGES OR OTHER
%	LIABILITY, WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE, ARISING FROM,
%	OUT OF OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR OTHER DEALINGS IN
%	THE SOFTWARE.
%	
%
%-----------------------------------------------------------------------------------------------------------------------------------------------%

%----------------------------------------------------------------------------------------
%	DOCUMENT DEFINITION
%----------------------------------------------------------------------------------------

% article class because we want to fully customize the page and not use a cv template
\documentclass[a4paper,11pt]{article}

%----------------------------------------------------------------------------------------
%	PACKAGES
%----------------------------------------------------------------------------------------
\usepackage{url}
\usepackage{parskip} 	

%other packages for formatting
\RequirePackage{color}
\RequirePackage{graphicx}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage[scale=0.91]{geometry}

%tabularx environment
\usepackage{tabularx}

%for lists within experience section
\usepackage{enumitem}

% centered version of 'X' col. type
\newcolumntype{C}{>{\centering\arraybackslash}X} 

%to prevent spillover of tabular into next pages
\usepackage{supertabular}
\usepackage{tabularx}
\newlength{\fullcollw}
\setlength{\fullcollw}{0.47\textwidth}

%custom \section
\usepackage{titlesec}				
\usepackage{multicol}
\usepackage{multirow}

%CV Sections inspired by: 
%http://stefano.italians.nl/archives/26
\titleformat{\section}{\Large\scshape\raggedright}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{6pt}{6pt}

%for publications
%\usepackage[style=authoryear,sorting=ynt, maxbibnames=2]{biblatex}

%Setup hyperref package, and colours for links
\usepackage[unicode, draft=false]{hyperref}
\definecolor{linkcolour}{rgb}{0,0.2,0.6}
\hypersetup{colorlinks,breaklinks,urlcolor=linkcolour,linkcolor=linkcolour}


%for social icons
%\usepackage{fontawesome5}

% job listing environments
\newenvironment{jobshort}[2]
    {
    \begin{tabularx}{\linewidth}{@{}X r@{}}
    \textbf{#1} & #2 \\[3.75pt]
    \end{tabularx}
    }
    {
    }

\newenvironment{joblong}[2]
    {
    \begin{tabularx}{\linewidth}{@{}X r@{}}
    \textbf{#1} & #2 \\[3.75pt]
    \end{tabularx}
    \begin{minipage}[t]{\linewidth}
    \begin{itemize}[nosep,after=\strut, leftmargin=1em, itemsep=1pt,label=--]
    }
    {
    \end{itemize}
    \end{minipage}    
    }

%----------------------------------------------------------------------------------------
%	BEGIN DOCUMENT
%----------------------------------------------------------------------------------------
\begin{document}

% non-numbered pages
\pagestyle{empty} 

%----------------------------------------------------------------------------------------
%	TITLE
%----------------------------------------------------------------------------------------

\begin{tabularx}{\linewidth}{@{} C @{}} \Huge{Manish Pariyar} \\[4pt]
\large{Customer Service Professional $|$ Sales Executive} \\[4pt]
\href{mailto:pariyarmansih030@gmail.com}{pariyarmansih030@gmail.com} \ $|$ \ 
\href{tel:+971548889367}{+971 54 888 9367} \ $|$ \ 
\href{https://www.linkedin.com/in/manish-pariyar/}{linkedin.com/in/manish-pariyar} \ $|$ \ 
\href{https://maps.google.com/?q=Dubai,+UAE}{Dubai, UAE} \\
\end{tabularx}

%----------------------------------------------------------------------------------------
% PROFESSIONAL SUMMARY
%----------------------------------------------------------------------------------------

\section{Professional Summary}
Customer-focused professional with experience in aviation, international event operations, and retail sales. Skilled in delivering excellent service, assisting diverse customers, and maintaining professionalism in fast-paced environments. Strong communication skills, cultural awareness, and a service-oriented personality. Seeking an opportunity to contribute to a dynamic organization while providing high-quality customer experiences.

%----------------------------------------------------------------------------------------
%	CORE SKILLS
%----------------------------------------------------------------------------------------
\section{Core Skills}

Customer Service Excellence, Sales \& Customer Engagement, Active Listening, Communication \& Interpersonal Skills, Cultural Intelligence, Teamwork \& Collaboration, Problem Solving, Professional Grooming \& Presentation

%----------------------------------------------------------------------------------------
% WORK EXPERIENCE
%----------------------------------------------------------------------------------------

\section{Professional Experience}

\begin{joblong}{Sales Executive $|$ \normalfont\textit{Buddha Thanka Treasure, Kathmandu}}{Sep 2023 -- Dec 2025}
\item Assisted customers in selecting products and provided product knowledge.
\item Maintained excellent customer service to increase satisfaction.
\item Achieved sales targets through effective customer engagement.
\item Maintained store presentation and organized merchandise.
\end{joblong}

\begin{joblong}{Customer Service Agent (Internship) $|$ \normalfont\textit{Civil Aviation Authority of Nepal (CAAN)}}{May 2023 -- Aug 2023}
\item Assisted passengers with check-in guidance and boarding procedures at Tribhuvan International Airport.
\item Provided accurate flight and airport information to travelers.
\item Supported airport staff in maintaining smooth passenger flow.
\item Maintained professionalism while handling passenger inquiries.
\end{joblong}

\begin{joblong}{Customer Service Agent $|$ \normalfont\textit{Urban Hospitality Service – Qatar Rail}}{Nov 2022 -- Jan 2023}
\item Assisted international passengers with metro and travel information during FIFA World Cup 2022.
\item Provided customer support during high passenger traffic.
\item Managed passenger flow and ensured smooth operations.
\item Resolved passenger concerns in a professional manner.
\end{joblong}

\begin{joblong}{Customer Service Executive $|$ \normalfont\textit{Buddha Thanka Treasure, Kathmandu}}{Jan 2019 -- Feb 2022}
\item Provided customer assistance and handled product inquiries.
\item Delivered excellent service to both local and international visitors.
\item Managed customer concerns and ensured customer satisfaction.
\item Supported daily store and sales operations.
\end{joblong}

%----------------------------------------------------------------------------------------
%	EDUCATION
%----------------------------------------------------------------------------------------
\section{Education}
\begin{tabularx}{\linewidth}{@{}X l@{}}
\textbf{Northern Light Academy of Aviation and Technology} & 2022 \\
Level 2 Diploma in Air Cabin Crew & \\
\textbf{Divya Gyan College of Management} & 2019 \\
Higher Secondary Education (+2) & \\ 
\textbf{Divya Gyan Higher Secondary School} & 2017 \\
School Leaving Certificate (SEE) & \\
\end{tabularx}

%----------------------------------------------------------------------------------------
%	CERTIFICATIONS & LANGUAGES
%----------------------------------------------------------------------------------------
\section{Certifications \& Languages}
\begin{tabularx}{\linewidth}{@{}l X@{}}
\textbf{Certifications} & \normalsize{Basic Fire Safety Training (2022), First Aid \& Medical Emergency Care (2022), Swimming and Ditching Drill (2022), Barista Training (2026)} \\
\textbf{Languages} & \normalsize{Nepali (Fluent), English (Fluent), Hindi (Fluent)} \\
\end{tabularx}



\begin{center}
\footnotesize Last updated: \today
\end{center}
\end{document}
